---
title: "Alcohol vs Seat choice"
author: "Cheyenne Toliver"
date: "Spring 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
 Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
 you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

This boxplot shows that the heavy drinker sit mainly in the back.   

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

This summary is telling me that most of the people who sat in the back drink a greater amount of alcohol when compared to people in the front and middle.   

## Inferential Tests

# Inferential

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The p-value is so small that it is unlikely that alcohol consumption in all three seats is the same.   

## When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
```

The TukeyHSD plot shows that people in the back drink alot more than the people in the front; It shows that the people in the middle drink less than the people in the back; The Middle-Front shows no evidence of difference in average alcohol consumption.   


## Conclusions

There is a difference in alcohol consumption and based on the evidence presented, people who sit in the back consume more than those who sit in the middle and front.   
